 

### 2024-04-16 outputs/paper.qmd
check

---
title: " "
author: Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Funding_Fuels_the_HIV-AIDS_Fight.git. Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1783/"
date: "April 2, 2024"
date-format: long
abstract: " "
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

## Variables
In progress

# Results
In progress

>>>>

---
title: " "
author: Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Tracing_Hidden_Struggles_of_Rural_Indian_Women_during_Pandemic.git. Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1783/"
date: "April 2, 2024"
date-format: long
abstract: " "
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

## Variables

# Results

```{r}
#| message: false
#| echo: false
# Install packages we need
library(plm)
library(lmtest)
library(sandwich)
library(stargazer)
library(glmnet)
library(dplyr)
library(haven)
library(readstata13)

# Set file paths
data_path <- "/cloud/project/data/raw_data/"
data_file <- paste0(data_path, "covid_gender_data.dta")

data <- read_dta(data_file)
```

```{r}
library(knitr)
library(kableExtra)

# Create a data frame that mimics the structure of the table in the uploaded image
data <- data.frame(
  Containment = c("0.242** (0.113)", "0.233*** (0.0698)", "0.361* (0.178)", "0.363*** (0.120)", 
                  "0.259 (0.156)", "0.237*** (0.0718)", "0.287* (0.141)", "0.276*** (0.0720)", 
                  "0.149 (0.150)", "0.127 (0.128)"),
  `Past Containment Controls` = rep("Yes", 10),
  `State FE` = rep("Yes", 10),
  `Age FE` = rep("Yes", 10),
  `Lasso Controls` = c(rep("No", 5), rep("Yes", 5)),
  `Case and Death Controls` = c(rep("No", 7), "Yes", "No", "Yes"),
  `Dep Var. Mean` = c(rep("0.344", 2), rep("0.276", 2), "0.301", "0.301", "0.307", "0.307", "0.299", "0.299"),
  `Adjusted R-squared` = c("0.009", "0.027", "0.022", "0.056", "0.023", "0.052", "0.021", "0.059", "0.006", "0.026"),
  Observations = rep("489", 10)
)

# Transpose the data frame to get the desired layout
transposed_data <- t(data)
colnames(transposed_data) <- c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
          "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations")

# Generate the kable table with rotated row headers
kable_output <- kable(transposed_data, "html", booktabs = TRUE, escape = FALSE, align = 'c') %>%
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "center") %>%
  row_spec(0, angle = 90, valign = "top") %>%
  add_header_above(c(" " = 1, "More Depressed" = 2, "More Exhausted" = 2, "More Anxious" = 2, "MH Index" = 2, "Less Safe" = 2)) %>%
  column_spec(1, bold = TRUE)

# Print the kable table
kable_output

```
```{r}
library(knitr)
library(kableExtra)

# Create a data frame that mimics the structure of the table in the uploaded image
data <- data.frame(
  ` ` = c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
          "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations"),
  X1 = c("0.242** (0.113)", "Yes", "Yes", "Yes", "No", "No", "0.344", "0.009", "489"),
  X2 = c("0.233*** (0.0698)", "Yes", "Yes", "Yes", "Yes", "No", "0.344", "0.027", "489"),
  X3 = c("0.361* (0.178)", "Yes", "Yes", "Yes", "No", "No", "0.276", "0.022", "489"),
  X4 = c("0.363*** (0.120)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.276", "0.056", "489"),
  X5 = c("0.259 (0.156)", "Yes", "Yes", "Yes", "No", "No", "0.301", "0.023", "489"),
  X6 = c("0.237*** (0.0718)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.301", "0.052", "489"),
  X7 = c("0.287* (0.141)", "Yes", "Yes", "Yes", "No", "No", "0.307", "0.021", "489"),
  X8 = c("0.276*** (0.0720)", "Yes", "Yes", "Yes", "Yes", "No", "0.307", "0.059", "489"),
  X9 = c("0.149 (0.150)", "Yes", "Yes", "Yes", "No", "No", "0.299", "0.006", "489"),
  X10 = c("0.127 (0.128)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.299", "0.026", "489")
)

# Transpose the data frame to get the desired layout
transposed_data <- t(data)
colnames(transposed_data) <- transposed_data[1, ]
transposed_data <- transposed_data[-1, ]

# Generate the kable table
kable_output <- kable(transposed_data, caption = "Table 1\nRelationship between Containment and Female Well-being.",
                      booktabs = TRUE, escape = FALSE) %>%
  kable_styling(full_width = FALSE, position = "center", font_size = 12) %>%
  column_spec(1, bold = TRUE, border_right = TRUE) %>%
  add_header_above(c(" " = 1, "More Depressed" = 1, "More Exhausted" = 1, "More Anxious" = 1, "MH Index" = 1, "Less Safe" = 5))

kable_output

```
```{r}
library(knitr)
library(kableExtra)

# Create a data frame that mimics the structure of the table in the uploaded image
data <- data.frame(
  ` ` = c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
          "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations"),
  X1 = c("0.242** (0.113)", "Yes", "Yes", "Yes", "No", "No", "0.344", "0.009", "489"),
  X2 = c("0.233*** (0.0698)", "Yes", "Yes", "Yes", "Yes", "No", "0.344", "0.027", "489"),
  X3 = c("0.361* (0.178)", "Yes", "Yes", "Yes", "No", "No", "0.276", "0.022", "489"),
  X4 = c("0.363*** (0.120)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.276", "0.056", "489"),
  X5 = c("0.259 (0.156)", "Yes", "Yes", "Yes", "No", "No", "0.301", "0.023", "489"),
  X6 = c("0.237*** (0.0718)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.301", "0.052", "489"),
  X7 = c("0.287* (0.141)", "Yes", "Yes", "Yes", "No", "No", "0.307", "0.021", "489"),
  X8 = c("0.276*** (0.0720)", "Yes", "Yes", "Yes", "Yes", "No", "0.307", "0.059", "489"),
  X9 = c("0.149 (0.150)", "Yes", "Yes", "Yes", "No", "No", "0.299", "0.006", "489"),
  X10 = c("0.127 (0.128)", "Yes", "Yes", "Yes", "Yes", "Yes", "0.299", "0.026", "489")
)

row_headers <- c("Containment", "Past Containment Controls", "State FE", "Age FE", "Lasso Controls", 
                 "Case and Death Controls", "Dep Var. Mean", "Adjusted R-squared", "Observations")

transposed_data <- as.data.frame(t(data[-1])) # Exclude the first column which has the headers
# Now set the names of the data frame based on the first column of 'data'
names(transposed_data) <- data$Header

# We don't set row names here, because after transposition, they are the column headers
# If you want to rotate the headers, that would be done in the PDF or HTML output, not in the data frame itself

# Create the kable, assuming it's going to be an HTML table
kable_output <- kable(transposed_data, format = "html", escape = FALSE) %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  add_header_above(c(" " = 1, "More Depressed" = 1, "More Exhausted" = 1, "More Anxious" = 1, 
                     "MH Index" = 1, "Less Safe" = 5)) # Adjust the span to match the structure of your table

# Print the kable table
kable_output
```
###
